\documentclass{article}

\title{User stories}
\date{}
\author{}
\begin{document}
\maketitle

\section{User story 1}
\textbf{As a} regular user,
\\\textbf{I want} to require a login page
\\\textbf{So that} unauthorized users cannot view the information.

\section{User story 2}
\textbf{As a} system engineer,
\\\textbf{I want} to compare properties of systems
\\\textbf{So that} I can spot the differences.

\section{User story 3}
\textbf{As a} system engineer,
\\\textbf{I want} to be able to search through all server information
\\\textbf{So that} I can quickly filter on specific terms.

\section{User story 4}
\textbf{As a} user,
\\\textbf{I want} to export system information in a human-readable format
\\\textbf{So that} I can compare it with previous results and keep a local archive.

\section{User story 5}
\textbf{As a} user,
\\\textbf{I want} to filter on multiple properties
\\\textbf{So that} I can only look at systems that match those properties.

\section{User story 6}
\textbf{As a} developer,
\\\textbf{I want} to have an OpenAPI specification
\\\textbf{So that} I can interface with the data.

\section{User story 7}
\textbf{As a} monitor,
\\\textbf{I want} to have Prometheus metrics about core properties of the CMDB
\\\textbf{So that} we can create alerting rules (backend requirement).

\section{User story 8}
\textbf{As a} system engineer,
\\\textbf{I want} to see when data was last collected per server.

\section{User story 9}
\textbf{As a} system engineer,
\\\textbf{I want} to see any errors that occurred during data collection on a particular system.

\section{User story 10}
\textbf{As a} system engineer,
\\\textbf{I want} to see hardware information of a system in a rack that is powered off
\\\textbf{So that} I can see what spare hardware is available.

\section{User story 11}
\textbf{As a} system engineer,
\\\textbf{I want} to be able to manually remove hardware that has been physically removed from a rack
\\\textbf{So that} any hardware that has been removed also gets removed from the CMDB.

\section{User story 12}
\textbf{As a} system engineer,
\\\textbf{I want} an overview of all our systems based on search criteria

\section{User story 13}
\textbf{As a} system engineer,
\\\textbf{I want} an overview of multiple servers and their attributes that I can choose myself
\\\textbf{So that} I can quickly make comparisons between hardware.

\section{User story 14}
\textbf{As a} system engineer,
\\\textbf{I want} to remove virtual systems from the CMDB when destroying the VM in Terraform
\\\textbf{So that} VMs that no longer exist are automatically removed from the CMDB.

\section{User story 15}
\textbf{As a} system engineer,
\\\textbf{I want} to be able to view all system information of a particular system
\\\textbf{So that} I can view detailed information of the system.

\end{document}
